### 2021-07-24 paper.tex
numbered sections and section names are not in center

% sections on new page
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}
\setcounter{secnumdepth}{0}

@@

	% certificate page
	\section[certificate]{\hfill \Huge Certificate \hfill}
	%\thispagestyle{empty}

@@

	\section[acknowledgement]{\hfill \Huge Acknowledgement \hfill}
	\label{sec:Acknowledgement}

@@

	% abstract
	\section[abstract]{}

@@

		\vspace{0.4cm}
		\large
		Using various machine learning models to detect brain tumor.

		\vspace{0.5cm}
		\textbf{Abstract}
	\end{center}

@@

	\section[introduction]{\hfill \Huge Introduction \hfill}
	\subsection[domain description]{Domain Description}

@@

	\section[background]{\hfill \Huge Background \hfill}

@@

	\section[methodology]{\hfill \Huge Methodology \hfill}

@@

	%\subsection{VGG 16}

	\section[implementation]{\hfill \Huge Implementation \hfill}

>>>>

% sections on new page
\usepackage{titlesec}
\newcommand{\sectionbreak}{\clearpage}
%\setcounter{secnumdepth}{0}

@@

	% certificate page
	\section*{\hfill \Huge Certificate \hfill}
	%\thispagestyle{empty}

@@

	\section*{Acknowledgement}
	\label{sec:Acknowledgement}

@@

	% abstract
	\section[abstract]{Abstract}

@@

		\vspace{0.4cm}
		\large
		Using various machine learning models to detect brain tumor.
	\end{center}

@@

	\section[introduction]{Introduction}
	\subsection[domain description]{Domain Description}

@@

	\section[background]{Background}

@@

	\section[methodology]{Methodology}

@@

	\subsection{VGG 16}

	VGG 16 is is a significantly more accurate ConvNet architecture, which not
	only achieve state-of-the-art accuracy on ILSVRC classification and
	localisation tasks, but are also applicable to other image recognition
	datasets, where they achieve excellent performance even when used as a part
	of a relatively simple pipelines (e.g. deep features classified by a linear
	SVM without fine-tuning).

	\subsubsection{Architecture}
	\label{sssec:vgg arch}

	During training, the input to our ConvNets is a fixed-size 224 × 224 RGB
	image. The only pre- processing we do is subtracting the mean RGB value,
	computed on the training set, from each pixel.  The image is passed through
	a stack of convolutional (conv.) layers, where we use filters with a very
	small receptive field: 3 × 3 (which is the smallest size to capture the
	notion of left/right, up/down, center). In one of the configurations we also
	utilise 1 × 1 convolution filters, which can be seen as a linear
	transformation of the input channels (followed by non-linearity). The
	convolution stride is fixed to 1 pixel; the spatial padding of conv. layer
	input is such that the spatial resolution is preserved after convolution,
	i.e. the padding is 1 pixel for 3 × 3 conv. layers. Spatial pooling is
	carried out by five max-pooling layers, which follow some of the conv.
	layers (not all the conv. layers are followed by max-pooling). Max-pooling
	is performed over a 2 × 2 pixel window, with stride 2.

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.5\linewidth]{imgs/vgg16_arch.png}
		\caption{VGG Architecture}%
		\label{fig:vgg_arch}
	\end{figure}

	A stack of convolutional layers (which has a different depth in different
	architectures) is followed by three Fully-Connected (FC) layers: the first
	two have 4096 channels each, the third performs 1000- way ILSVRC
	classification and thus contains 1000 channels (one for each class). The
	final layer is the soft-max layer. The configuration of the fully connected
	layers is the same in all networks.

	All hidden layers are equipped with the rectification (ReLU) non-linearity.
	We note that none of our networks (except for one) contain Local Response
	Normalisation (LRN) normalisation: as will be shown in Sect. 4, such
	normalisation does not improve the performance on the ILSVRC dataset, but
	leads to increased memory con- sumption and computation time. Where
	applicable, the parameters for the LRN layer are those of.

	\subsubsection{Configuration}

	The ConvNet configurations, evaluated in this paper, are outlined in Table
	1, one per column. In the following we will refer to the nets by their names
	(A–E).  All configurations follow the generic design presented in
	Section~\ref{sssec:vgg arch} and differ only in the depth: from 11 weight
	layers in the network A (8 conv. and 3 FC layers) to 19 weight layers in the
	network E (16 conv. and 3 FC layers). The width of conv. layers (the number
	of channels) is rather small, starting from 64 in the first layer and then
	increasing by a factor of 2 after each max-pooling layer, until it reaches
	512.

	\begin{figure}[h]
		\centering
		\includegraphics[width=0.8\linewidth]{imgs/vgg16_conf}
		\caption{VGG16 configuration}%
		\label{fig:vgg16_conf}
	\end{figure}

	\section[implementation]{Implementation}
